\documentclass[a4paper]{article}
\author{Ryan Thomas}
\title{Resume of Ryan Thomas}
\date{20-May-2009}

\addtolength{\hoffset}{-1.0cm}
\addtolength{\textwidth}{2.0cm}
\addtolength{\voffset}{-3.0cm}
\addtolength{\textheight}{4.6cm}
\pagestyle{plain}

\begin{document}

\newcommand{\ryanHeader}{
\begin{center}
\rule{14.1cm}{0.5mm}
\end{center}
\vspace{-0.6cm}
\begin{center}
\textsc{Ryan Thomas}
\end{center}
\vspace{-0.3cm}
18 St Andrews Dr\hspace{7.8cm} Mobile: 0414 325 379\\
Glenmore Park, N.S.W. 2745 \hspace{4.7cm} Email: r.n.thomas@gmail.com
\vspace{-0.3cm}
\begin{center}
\rule{14.1cm}{0.5mm}
\end{center}}

\ryanHeader

\section*{Profile}
A software engineer specialising in object-oriented design and analysis with experience in the full software development life cycle process including requirements definition, design, prototyping, proof-of-concept, interface implementation, testing and maintenance.
\begin{itemize}
\item Strong knowledge of the Java language.
\item Solid time management skills, demonstrated proficiency in working on multiple projects simultaneously.
\item Ability to adapt to a constantly changing environment and overcome challenges encountered.
\item Capacity to work as a proficient team member and provide support where required.
\item Confident public speaker and presenter.
\end{itemize}

\section*{Skills and Technical Experience}
\begin{tabular}{l l}
\textbf{Languages:} & Java, C++, SQL, XML, JavaScript, JSP, \LaTeX, Python\\
\textbf{Frameworks:} & Spring, Hibernate, SiteMesh, JDBC, JUnit, Lucene, jQuery\\
\textbf{IDEs:} & IntelliJ, Netbeans, Eclipse, Borland C++ Builder\\
\textbf{Databases:} & Oracle 10, SQLServer 2000, mysql\\
\textbf{Web Servers:} & Apache, Tomcat, WebSphere\\
\textbf{Operating Systems:} & OS X, Windows, Linux (2.4 \& 2.6 kernels), FreeBSD\\
&\\
\textbf{Vehicle Licence:}&MR, R\\
\textbf{ADF Security}&\\\textbf{Clearance Level:}&Confidential\\
\textbf{Flight Time:}&178.2hrs Total --- 23.3hrs IF, 15.8hrs Command, 10.9hrs Night
\end{tabular}

\vspace{5pt}
\section*{Professional Experience}

\textbf{Atlassian Software Systems, Sydney, N.S.W.\\Software Engineer\\December 2009 --- Current}\\\\
I am currently employed by Atlassian as a Software Engineer working on the Confluence Enterprise Wiki. My role involves design and development of various features inside of Confluence and our plugins as well as liaising with the plugin developer ecosystem.\\\\
I have spoken at AtlasCamp, the Atlassian annual developers conference, on how we are supporting the plugin developer ecosystem in the latest version of Confluence and how we are going to make it easy for developers to migrate their products.\\\\
I have been awarded the Performance Engineering Award for my work in adding distributed filesystem support to the already in place clustering support of Confluence and have replaced the Oracle Coherence distributed caching with Hazelcast, an open source solution.

\newpage
\ryanHeader

\section*{Professional Experience continued}
\textbf{Objective Corporation Limited, North Sydney, N.S.W.\\Software Engineer / Enterprise Search Specialist\\August 2009 --- December 2009}\\\\
The Objective Software Suite is a number of J2SE services communicating via CORBA to provide Enterprise Content Management to users and to manage documents in the order of hundreds of terabytes.\\\\
My role at Objective Corporation was to take ownership of the search and indexing services of the Objective Software Suite and provide guidance and support for the current and future implementations. These services utilise Verity's K2 search server and I was tasked with investigating and prototyping a replacement; with Apache Solr being the selected at the time.\\\\
I left Objective in December of 2009 to take a position with Atlassian Software Systems.\\\\
\textbf{Australian Defence Force --- Army\\Trainee Pilot\\March 2008 --- June 2009}\\\\
I was employed as a trainee pilot in the Australian Army after completing the rigorous selection process demanded by the ADF Pilot Selection Agency. On completion of the fixed wing training in Tamworth my wife and I decided that my being employed in the Army, and due to a number of personal factors it would be best if I pursued work back in the software field.\\\\
The flight training was conducted at the Australian Defence Force Basic Flying Training School in Tamworth N.S.W. I hold a military endorsement on the PAC CT-4B aircraft for day and night operations.\\\\
The training I have received from the Army has given me experience in the management of personnel on the ground, in a multi-crew airborne environment and in the making of time critical decisions.\\\\
\textbf{Oracle Corporation, North Ryde, N.S.W.\\Senior Software Engineer\\March 2007 --- March 2008}\\\\
My work at Oracle was focused on developing a search framework for the Hyperion Workspace product. This framework involved the use of the Lucene search library which we distributed over multiple nodes. We developed an interface to handle the large variety of document types that could be imported into the Hyperion Workspace as well as multiple node synchronisation for the indexing and searching tasks.\\\\
Due to the nature of the Hyperion Workspace we had to be able to parse and index a large number of different document types, including common Microsoft and Adobe formats to Hyperion Dashboards and Financial Reports documents.\\\\
As well as developing the search functionality I was tasked with concurrently writing a plugin for the Oracle Secure Enterprise Search application that would allow it to query the Lucene index we had created for the Hyperion Workspace product.\\\\

\newpage
\ryanHeader

\section*{Professional Experience continued}
\textbf{Hyperion Solutions, North Sydney, N.S.W.\\Software Engineer\\December 2005 --- March 2007} \\\\
\emph{Hyperion Solutions was acquired by Oracle Corporation in March of 2007.}\\\\
Hyperion Solutions was the world leader in Business Intelligence and Business Performance Management software until being acquired by Oracle Corporation in March of 2007.\\\\
My role at Hyperion was to develop, document and test software for the Impact Manager line of products. The Impact Manager product line is a collection of software designed to run on a number of Java application servers and provides a web-based interface to the user for most of Hyperions BI\&BPM software.\\\\
Initially my role was focused on developing front end components for our Dashboard Builder line of products which involved the use of Javascript and VB, on showing an interest in the server side development I was moved onto the server team. On the server team we developed a set of change management tools for the Hyperion Workspace product in Java, utilising CORBA for communication between the multiple nodes and the front end. Database interactions were done using an in house ORM solution designed to interact with Oracle, SQL Server and IBM DB2 databases.\\\\
\textbf{TransActive Systems, Gosford, N.S.W.\\Software Developer / Technical Support\\July 2004 --- December 2005}\\\\
TransActive Systems was the leading developer in financial professional (mortgage broking) software for both front-end and back office solutions. TransActive Solutions developed client-server solutions, web-based applications as well as providing business-to-business web services.\\\\
I was employed by TransActive Systems whilst completing the remaining 6 months of my degree program part-time. My duties at TransActive involved the design, development and maintenance of both client side applications (all C++ based) and all of the Java based server side code. During my time at TransActive I migrated the previous server system (Java servlet / Apache Tomcat) to a J2EE (EJB) solution running on the JBoss application server.\\\\
Further duties included writing user and technical documentation for all of the changes made or applications developed; they also included liaising with external sources for the integrations of a range of back end systems and assisting in user training sessions. As TransActive was only a small company, full technical support was expected from each employee.\\\\
\textbf{BAE Systems, Williamtown, N.S.W.\\Software Development (work experience)\\July --- September 2003}\\\\
A requirement for my degree program was to complete industrial work experience --- this was completed with BAE Systems at RAAF Base Williamtown. This experience was organised through my software engineering mentor, which is part of the industry mentoring scheme at the University of Newcastle. During my five weeks at BAE Systems I worked on Project Wedgetail, which is the development of an Airborne Early Warning \& Communications (AEW\&C) system for the Boeing 737 platform.
\newpage
\ryanHeader

\section*{Education}
\textbf{Masters of Information Technology --- Knowledge Systems \& Data Mining}\\
The University of New South Wales, Australia. 2006 --- \emph{Currently Studying}\\\\
\textbf{Bachelor of Engineering --- Software Engineering}\\
The University of Newcastle, Australia. 2001 --- 2005\\\\
\textbf{Certificate III --- Resource Operations}\\
Australian Army, September 2005\\\\
\textbf{Certificate III --- Business $($Frontline Management$)$}\\
Australian Army, September 2005\\\\
\textbf{Certificate III --- Government}\\
Australian Army, September 2005\\\\
\textbf{Certificate III --- Transport \& Distribution (Road Transport)}\\
Australian Army, April 2002\\\\
\textbf{Statement of attainment towards\\Certificate IV --- Assessment and Workplace Training}
\begin{itemize}
\item Train Small Groups.
\item Deliver Training Sessions.
\end{itemize}
Australian Army, September 2005\\\\
\textbf{Higher School Certificate}\\
Corpus Christi College, Tuggerah. 1999 --- 2000

\vspace{5pt}
\section*{Professional Credentials}
\textbf{Professional Member}\\
Association for Computing Machinery\\
2005 --- Present\\\\
\textbf{Bombardier}\\
Royal Australian Artillery, Australian Army Reserve\\
2000 --- 2010\\\\
\textbf{Professional Member (Graduate) --- Lapsed}\\
Institute of Engineers Australia

\newpage
\ryanHeader

\section*{Referees}
\textbf{Olivier Louchart-Fletcher}\\
Principal Software Engineer\\
Oracle Corporation\\\\
\begin{tabular}{@{}l l}
Phone:&$($02$)$ 9491 1487\\
Mobile:&0406 721 192\\
Email:&olivier.louchart-fletcher@oracle.com\\
\end{tabular}
\\\\\\
\textbf{William Dampney}\\
Software Engineer\\
The University of Newcastle\\\\
\begin{tabular}{@{}l l}
Mobile:&0409 774 605\\
Email:&william.dampney@newcastle.edu.au\\
\end{tabular}
\end{document}
